{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
added one more property about the attacker
colon instead of fullstop in formular
beautified definitions

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of security levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$.

@@

\begin{align*}
s, h \Downarrow_{conc} \mu \Leftrightarrow \exists s', h'.\ (s,h \leadsto_{conc}^* s',h') \land s'.act = \emptyset \land s'.gmem = \mu
\end{align*}

@@

\begin{definition}{sregion}
The control dependence region for a branching command $[c]^n$ in the source language is
defined as the labels inside the branching command, except for those ones that are inside a
\texttt{fork} command.
\end{definition}

@@

\begin{definition}{tregion}
$tregion(n)$ is defined as the set of instruction labels obtained by compiling the commands
$[c']^{n'}$ of the branching instruction $[c]^n$ of the source code with a compilation function $\mathcal{C}$.
\end{definition}

@@

\begin{definition}{jun}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

\begin{definition}{next}
For every branching point $c$ in the source program such that $\vdash_\circ [c]_\bullet^n$, we  have
that $\forall k \in tregion(n) .\ next(k) = jun(n)$.
\end{definition}

>>>>

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of security levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$. It is also assumed, that access
control works correctly (i.e. the attacker can not access $high$ elements
directly).

@@

\begin{align*}
s, h \Downarrow_{conc} \mu \Leftrightarrow \exists s', h':\ (s,h \leadsto_{conc}^* s',h') \land s'.act = \emptyset \land s'.gmem = \mu
\end{align*}

@@

\begin{definition}
The control dependence region $sregion(n)$ for a branching command $[c]^n$ in the source language is
defined as the labels inside the branching command, except for those ones that are inside a
\texttt{fork} command.
\end{definition}

@@

\begin{definition}
$tregion(n)$ is defined as the set of instruction labels obtained by compiling the commands
$[c']^{n'}$ of the branching instruction $[c]^n$ of the source code with a compilation function $\mathcal{C}$.
\end{definition}

@@

\begin{definition}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

\begin{definition}
For every branching point $c$ in the source program such that $\vdash_\circ [c]_\bullet^n$, the next function
is defined as $\forall k \in tregion(n) .\ next(k) = jun(n)$.
\end{definition}
